Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-24 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Captions and description for network of users

Using the Noe4J graph database and the Cypher query language when monitoring the experiments provided 
views on the connected data difficult to replicate in a relational database. An example view is presented 
in figure \ref{fig:users-graph} showing comparasion between two users on the degree of the 
{\tt has} relationship.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{}
    \label{}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{}
    \label{}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Top ranked number individuals rated by user using a
     logarithmic scale.}
    \label{fig:top-ranked-participation}
\end{figure*}

>>>>

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Top ranked number individuals rated by user using a
     logarithmic scale.}
    \label{fig:top-ranked-participation}
\end{figure*}

Using the Noe4J graph database and the Cypher query language when monitoring the experiments provided 
views on the connected data difficult to replicate in a relational database. As an example, when comparing the
deployments B and GG based on their network of users (shown in figures \ref{fig:B-network} and \ref{fig:GG-network}
respectivly) additionaly to the differences in the number of nodes, certain patterns can also be observed.
